Project-I by Group MexicoCity

### 2014-11-03 report/paper.tex
final update - fix
final update with corrections .----------------------------.

\subsection{Ridge Regression}
After applying least squares, we have also done a cross validation using seeds. The result is shown in Figure \ref{fig:ridreggcv}.
\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{images/ridgeRegCV.jpg}
\caption{Cross validation : Ridge regression with different lambda values }
\label{fig:ridreggcv}
\end{figure}
We realized that the RMSE decreased for a parameter $\lambda = 39.0694$ to a RMSE of $0.3073$. We can see that on the Figure \ref{fig:ridreggcv}.

@@

Adding back the mentioned dummy variables 44 and 47 actually increased the test error to 0.33105. This leads the matrix $\mathbf{\tilde{X}}$ to become ill conditioned.

@@

By isolating the 18th and 34th input variables, and producing polynomial transforms of them using the myPoly function, and then measuring their Pearson correlation coefficient with the output, we could see that the cube and the power 5 of the 18th variable, and powers up to 6 for the 34th variable are correlated with the output. When adding these feature transformations, we could lower the test error to 0.3307, which is quite lower now than the starting test error of 0.3805.
\section{Classification}
\subsection{visualization and cleaning}

@@

For the classification, the best method was penalized logistic regression. We obtained different results depending the type of error we computed. \begin{description}
\item[RMSE] We achieved a test error of 0.2644.
\item[01 loss]We achieved a test error of 0.09486.
\item[log loss] We achieved a test error of 0.25149.
\end{description}
With logistic regression we obtained different results depending the type of error we computed. \begin{description}
\item[rmse] We achieved a test error of 0.2644.
\item[01 loss]We achieved a test error of 0.09486.
\item[log loss] We achieved a test error of 0.2637.
\end{description}
We see that there is only a small improvement with the log loss error.
The best error we achieved is through the penalized logistic regression method and using the 0-1 loss error.

@@

\subsubsection*{References}
Kevin Murphy, Machine Learning : A Probabilistic Perspective {\em The MIT Press
Cambridge, Massachusetts
London, England,2012}

\end{document}

>>>>

@@

Adding back the mentioned dummy variables 44 and 47 actually increased the test error to 0.33105. Adding only the specifically mentioned (above) classes indicator dummy variables led the matrix $\mathbf{\tilde{X}}$ to become ill conditioned.

By isolating the 18th and 34th input variables, and producing polynomial transforms of them using the myPoly function, and then measuring their Pearson correlation coefficient with the output, we could see that the cube and the power 5 of the 18th variable, and powers up to 6 for the 34th variable are correlated with the output. When adding these feature transformations, we could lower the test error to 0.3307, which is quite lower now than the starting test error of 0.3805.

@@

\subsection{Ridge Regression}
After applying least squares, we have also done a cross validation using seeds. The result is shown in Figure \ref{fig:ridreggcv}.
\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{images/ridgeRegCV.jpg}
\caption{Cross validation : Ridge regression with different lambda values }
\label{fig:ridreggcv}
\end{figure}
We realized that the RMSE decreased for a parameter $\lambda = 39.0694$ to a RMSE of $0.3073$. We can see that on the Figure \ref{fig:ridreggcv}.
\section{Classification}
\subsection{visualization and cleaning}

@@

For the classification, the best method was penalized logistic regression. We obtained different results depending the type of error we computed. \begin{description}
\item[RMSE] We achieved a test error of 0.2644.
\item[01 loss]We achieved a test error of 0.09486.
\item[log loss] We achieved a test error of 0.25149.
\end{description}
With logistic regression we obtained different results depending the type of error we computed. \begin{description}
\item[rmse] We achieved a test error of 0.2644.
\item[01 loss]We achieved a test error of 0.09486.
\item[log loss] We achieved a test error of 0.2637.
\end{description}
We see that there is only a small improvement with the log loss error with penalized logistic regression.
The best error we achieved is through the penalized logistic regression method and using the 0-1 loss error.

@@

\subsubsection*{References}
Kevin Murphy, Machine Learning : A Probabilistic Perspective {\em The MIT Press
Cambridge, Massachusetts
London, England,2012}\\
Trevor Hastie,Robert Tibshirani,Jerome Friedman : The Elements of
Statistical Learning. Data Mining,Inference,and Prediction. {\em Springer, 2008}\\
Gareth James,
Daniela Witten,
Trevor Hastie,
Robert Tibshirani:An Introduction to Statistical Learning.{\em Springer, 2013}
\end{document}
